Refinements for open automata

### 2023-02-17 2021-Refinement/paper/refinementarticleV2.tex
Theorem 3

\TODO{Je reintroduis la notion de reachability et non introduction de blocage}
\subsection{Deadlock Reduction, Reachability, and Composition}

@@

\TODO{Fin reintrod.}

@@

The next  theorem states that if two automata are in refinement relation and the same automaton is placed in the same hole of the two automata, then the refinement is preserved. This is the first step toward proving that
 refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
The second part, i.e. proving that placing in the same context two open automata in refinement, we obtain two open automata in refinement is left for future works.
%
%
%The composition of $A_1$ and $A_3$ is a refinement of the composition of $A_2$ and $A_3$ provided $A_1$ is a refinement of $A_2$ and the hole in which we are composing inside $A_1$ and $A_2$ is tracked by the refinement relation.

\begin{theorem}[Context refinement]\label{thm:ContextRefinement}
Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_1}{A_2}{H}$. 
Let $J_3$ be the set of holes of $A_3$.
%Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
\end{theorem}

Pictorially, the theorem has the following form:

@@

The bisimulation relation that we consider is the one that makes $A_1$ and $A_2$ bisimilar, complemented with identity of configurations for $A_3$.
The proof relies on the fact that, by construction, all transitions of the composed automaton $A_1\subst{A_3}{k}$ are specified by open transitions of $A_1$. For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly. If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e., the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
\begin{example} The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata, depicted in Fig.~\ref{Fig:ComposeRefine}. As stated by the theorem,  it can easily be verified that this automaton is a refinement of the automaton of the figure Fig.~\ref{Def:CompOA}, i.e. the automaton resulting from the composition of the abstract \texttt{database}.
\end{example}

@@

This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$, then we have:
\begin{multline*}
 V_1 \uplus V_2 \uplus V_3  \vdash \underbrace{\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}_{R_{13}(s_1,s_3)} \implies  ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
 \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
\end{multline*}
By removing the $A_2$ variables that have not effect on $A_2$ et $A_3$,
we get the desired result:
\begin{multline*}
 V_1 \uplus  V_3  \vdash R_{13}(s_1,s_3) \implies  ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
 \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
\end{multline*}
\qed
\end{enumerate}
\section{Proof of Context Refinement (Theorem~\ref{thm:ContextRefinement})}
\begin{quote}
Suppose that $\wrel{A_1}{A_2}{H}$, \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking. We have: 
\[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
\end{quote}
\smallskip

@@

Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}

From the two previous formulas, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13} \land \reach{A_{13}}\mpar{s_{13}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}		\nwedge\\
			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
 \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}

@@

\paragraph{Second case: Only the encompassing automaton performs a transition}
 $t_{13}$ is obtained  by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
\]
We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
\[t_{23x} = \left(
\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]

@@

\item \RAB{Part in progress} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ R\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) 
\end{multline*}

@@

Similarly, transitions of $A_2$ are still transitions of $A_{23}$,  we get:
\begin{multline*}
V_{23}  \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_2}} \fguard{t_2}) \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
\end{multline*}
From these three formulas we deduce:
  \begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
\end{multline*}

@@

>>>>

\TODO{La section 4.1 reintroduit la notion de reachability et non introduction de blocage}
\subsection{Deadlock Reduction, Reachability, and Composition}

@@

\TODO{Fin reintroduction}

@@

The next  theorem states that if two automata are in refinement relation and the same automaton is placed in the same hole of the two automata, then the refinement is preserved. This is the first step toward proving that
 refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
The second part,  proving that placing in the same context two open automata in refinement, we obtain two open automata in refinement is left for future works.
%
%
%The composition of $A_1$ and $A_3$ is a refinement of the composition of $A_2$ and $A_3$ provided $A_1$ is a refinement of $A_2$ and the hole in which we are composing inside $A_1$ and $A_2$ is tracked by the refinement relation.

\begin{theorem}[Context refinement]\label{thm:ContextRefinement}
Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_1}{A_2}{H}$. 
Let $J_3$ be the set of holes of $A_3$ and suppose that $k \in H$.
%Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
\end{theorem}
\RAB{A t-on des conditions sur H?}

Pictorially, the theorem states the following result:

@@

The bisimulation relation that we consider is the one that makes $A_1$ and $A_2$ bisimilar, complemented with identity of configurations for $A_3$.
The proof relies on the fact that, by construction, all transitions of the composed automaton $A_1\subst{A_3}{k}$ are specified by open transitions of $A_1$. For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly. If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e., the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.

\begin{theorem}[Congruence]
Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
 $\wrel{A_1}{A_2}{H}$.  Let $J_3$ be the set of holes of $A_3$ and suppose that \(k \in H\).
We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
\end{theorem}

\begin{example} \RAB{cet exemple illustre plutot  que la composition est un raffinement, i.e.,  $\wrel{A_1\subst{A_2}{k}}{A_1}{J_1   \setminus \mbrc{k}}$ doit-on ajouter ce resultat comme un lemme?}

The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata, depicted in Fig.~\ref{Fig:ComposeRefine}. As stated by the theorem,  it can easily be verified that this automaton is a refinement of the automaton of the figure Fig.~\ref{Def:CompOA}, i.e. the automaton resulting from the composition of the abstract \texttt{database}.
\end{example}

@@

This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$, then we have:
\begin{multline*}
 V_1 \uplus V_2 \uplus V_3  \vdash \underbrace{\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}_{R_{13}(s_1,s_3)} \implies  ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
 \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
\end{multline*}
By removing the $A_2$ variables that have not effect on $A_2$ et $A_3$,
we get the desired result:
\begin{multline*}
 V_1 \uplus  V_3  \vdash R_{13}(s_1,s_3) \implies  ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
 \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
\end{multline*}
\qed
\end{enumerate}
\section{Proof of Context Refinement (Theorem~\ref{thm:ContextRefinement})}
\begin{quote}
Suppose that $\wrel{A_1}{A_2}{H}$, \(k \in H\) \cancel{and that \(A_1\subst{A_3}{k}\) is non-blocking}. We have: 
\[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
\end{quote}
\smallskip

@@

\RAB{ I think there is no need to the no blocking condition} Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge \cancel{\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge} \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}

From the two previous formulas, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13} \land \cancel{\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}		\nwedge\\
			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
 \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}

@@

\paragraph{Second case: Only the encompassing automaton performs a transition.}
 $t_{13}$ is obtained  by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
\]
We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
\[t_{23x} = \left(
\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]

@@

\item \TODO{To check this point:} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ R\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) 
\end{multline*}

@@

Similarly, transitions of $A_2$ are still transitions of $A_{23}$,  we get:
\begin{multline*}
V_{23}  \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_2}} \fguard{t_2}) \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
\end{multline*}
From the three previous formulas we deduce:
  \begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
\end{multline*}

@@

\section{Proof of Congruence}
Suppose $\wrel{A_2}{A_3}{H}$ and  $k \in H$. We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
\proof
Let us denote by $A_{12}$ (resp. $A_{13}$) the open automaton resulting from $A_1\subst{A_2}{k}$ (resp. $A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.

We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 = \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.

% The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement). In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.

Let $R$ be the refinement relation relating states of $A_2$ and $A_3$. 
Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
Consider any two states $s_{12} = \mpar{s_1,s^1_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming). We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
\[ R' \mpar{s_{12}, s_{13}} = R\mpar{s_{2}, s_{2}} \wedge \bigwedge_\subbox{v_1\in V_1}
 v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
Let us denote $H'=H\cup J_1 \setminus\{k\}$.
We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
\begin{enumerate}
\item \TODO{Pareil que le theorem precedent}

\item Second, we need to prove for any OT $t_{12}$ in $T_{12}$ originating from $s_{12}$

\begin{align*}
		&  \OTx{12}{}{12}{12} \in \fOT{s_{12}}
\end{align*}		
there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
\begin{align*}
		&  \mpar{\OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X}
\end{align*}	
such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
\begin{multline*}	
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{multline*}
By definition of composition and open automata refinement we have: 
\begin{align*}
&V_{12}= V^1_1\uplus V_3 \text{ and }
V_{13}= V^2_1\uplus V_3\\
& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13} \\
\end{align*}
We have by hypothesis $\wrel{A_2}{A_3}{H}$, then for any open transition $t_2$ in $T_2$  originating from $s_2$:
\begin{align*}
\OTx{2}{}{2}{2} \in \fOT{s_2}
\end{align*}
there exists an indexed family of OTs originating from $s_{2}$: 
\begin{align*}
\mpar{\OTx{3}{x}{3x}{3x} \in \fOT{s_{3}}}^{x \in X} 
\end{align*}
such that $\forall x \in X, J'_{3x} \cap H = J'_2 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ R\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \nwedge\\
			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
		\end{array}}  \qquad \quad (*)
\end{multline*}	
\smallskip

Consider any transition $t_{12}$ in $A_{12}$. Based on the definition of the composition  $t_{12}$ can be obtained from two different cases,  we will consider the two cases
separately.

\paragraph{First case: Both automata perform a transition.} The transition $t_{12}$  is obtained by the composition of transition $t_2=\OTx{2}{}{2}{2}$ and a transition \[t_1^1=
\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
\] The result:
%%%% Attention deactiver ici
\[
t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}',s'_2 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}{g^1_1 \wedge g_2 \wedge \alpha_2 = \beta^1_{1k}}{\psi^1_1 \uplus \psi_2} \qquad \text{ where } k \in {J^1_{1}}^{\prime} 
\]

We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (as stated above).
By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$.
\[
t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
\right)^{x\in X}\]
Recall that in this case  $k \in {J^1_{1}}^{\prime}$, so $\forall x \in X$ we have
\begin{align*}
  J'_{31x} \cap H'  
&=((J'_{3x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{1} ) \cap (H\uplus J_1 \setminus\{k\} )\\
&=((J'_{3x}\cap (H\uplus J_1))\uplus (J^{2 \prime}_{1}\cap (H\uplus J_1)))\setminus \mbrc{k}\\
&=((J'_{3x}\cap H)\uplus (J^{2 \prime}_{1}\cap  J_1))\setminus \mbrc{k}\text{ since } J_1\cap J'_{3x} = \emptyset \text{ and } H\cap J^{2 \prime}_{1} = \emptyset\\
& =((J'_{3x}\cap H)\uplus J^{2 \prime}_{1})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{1}\subseteq J_1\\
& =((J'_2\cap H)\uplus J^{1 \prime}_{1})\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
&= ((J'_2 \cap H) \uplus (J^{1 \prime}_{1} \cap J_1)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{1}\subseteq J_1\\ 
& = (J'_2\cap (J_1 \uplus H)) \uplus ((J^{1 \prime}_{1} \cap (J_1 \uplus H)) \setminus \mbrc{k} \text{ since } J_1\cap J'_{2} = \emptyset \text{ and } H\cap J^{1 \prime}_{1} = \emptyset\\
		& = \mpar{(J'_2  \uplus J^{1 \prime}_{1})\setminus \mbrc{k}} \cap \mpar{(J_{1} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{12} \cap H'
\end{align*}

=============================
\paragraph{Second case: Only the encompassing automaton performs a transition.}
* or by an the transition $t_1^2=
\OT{ s^2_1}{{s^2_1}'}{\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{ \psi^2_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
\[t_{12} = \OT{\mpar{s^2_1, s_2}}{\mpar{{s^2_1}', s'_2}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{1 \prime}_1} }}{g^2_1}{\psi^2_1}
\]
We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
\[t_{13x} = \left(
\OT{\mpar{s^1_1, s_3}}{\mpar{s^2_1,s'_{2x}}}{\alpha_{3x}}{\beta_{3xj}^{j \in J'_{3x}}}{g_{3x}}{\psi_{3x}} \right)^{x\in X}\]

~\qed
\end{enumerate}
